---
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---


## Steps

1. Set working directory and the file path to refer to the appropriate data set.

2. Set column names from the data set to a continuous varaible measure or discrete variable dimension.

3. After running the R code that creates the code for a SQLDeveloper table, create a NewYork table in SQL Developer and import the data from the csv data set.

4. for the first plot: after reading the file, wrangle and plot sex by count/number of deaths for each ethnicity in the year 2011.  Each dot represents a different cause of death.

5. For the second plot: Plot each ethnicity's percentage of death due to heart diseases for the years 2007 - 2011.  Each dot represents a different year's ethnicity's percent of death. Some years overlap with one another, which is why there aren't 5 full bullets per ethnicity.

6. For the third plot: Plots sex by count/number of deaths for each ethnicity in the year 2010.  Each dot represents a different cause of death. 


```{r}
source("../02DataWrangling/DV_RProject2.R", echo = TRUE)
```

### Head and Summary

```{r}
source("../01Data/Data.R")
```

